A Hybrid Neutronics Method for Time-Dependent Control Rod Modeling in Molten Salt Reactors

### 2024-06-20 hybrid.tex
Fix typos and add numerical implementation section

\noindent Time derivative term:
%
\begin{gather}
  \left(\left(\mathbb{I}+\bm{\tau}\mathbb{L}_1\right)\bm{\Psi}^*,
  \frac{\partial}{\partial t}\left(\frac{\bm{\Psi}}{\bm{v}}\right)\right) =
  \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\Psi^*_{g,d}+\tau_g\hat{\Omega}_d\cdot\Psi^*_{g,d},
  \frac{\Psi_{g,d}}{v_g}\right)_\mathcal{D}
\end{gather}
%
Streaming term:
%
\begin{gather}
  \left(\mathbb{L}_1\bm{\Psi}^*,
  \left(\bm{\tau}\mathbb{L}_1-\mathbb{I}+\bm{\tau}\mathbb{L}_2\right)\bm{\Psi}\right) =
  \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\hat{\Omega}_d\cdot\nabla\Psi^*_{g,d},\tau_g\hat{\Omega}
  \cdot\nabla\Psi_{g,d}-(1-\tau_g\Sigma_{t,g})\Psi_{g,d}\right)_\mathcal{D}
\end{gather}
%
Collision term:
%
\begin{gather}
  \left(\mathbb{L}_2\bm{\Psi}^*,\bm{\Psi}\right) =
  \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\Psi^*_{g,d},\Sigma_{t,g}\Psi_{g,d}\right)_\mathcal{D}
\end{gather}
%
Scattering term:
%
\begin{gather}
  \left(\left(\mathbb{I}+\bm{\tau}\mathbb{L}_1\right)\bm{\Psi}^*,\mathbb{S}\bm{\Psi}\right) =
  \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\Psi^*_{g,d}+\tau_g\hat{\Omega}_d\cdot\nabla\Psi^*_{g,d},
  \sum^G_{g'=1}\sum^L_{l=0}\Sigma^{g'\rightarrow g}_{s,l}\sum^l_{m=-l}
  \frac{2l+1}{w}Y_{l,m}(\hat{\Omega}_d)\phi_{g',l,m}\right)_\mathcal{D}
\end{gather}
%
Prompt fission source term:
%
\begin{gather}
  \left(\left(\mathbb{I}+\bm{\tau}\mathbb{L}_1\right)\bm{\Psi}^*,\mathbb{F}\bm{\Psi}\right) =
  \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\Psi^*_{g,d}+\tau_g\hat{\Omega}_d\cdot\nabla\Psi^*_{g,d},
  \frac{1}{w}\bar{\chi}_g\sum^G_{g'=1}\nu\Sigma_{f,g'}\phi_{g'}\right)_\mathcal{D}
\end{gather}
%
where $\bar{\chi}_g=\chi_{p,g}\left(1-\beta\right)$ for time-dependent problems with \glspl{DNP}
and $\bar{\chi}_g=\chi_{g}$ for steady-state problems without \glspl{DNP}.

@@

\noindent Vacuum boundary term:
%
\begin{gather}
  \langle\bm{\Psi}^*,\bm{\Psi}\rangle^+ - \langle\bm{\Psi}^*,\bm{\Psi}^\text{inc}\rangle^- =
  \begin{cases}
    \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\Psi^*_{g,d},
    \hat{\Omega}_d\cdot\hat{n}_b\Psi_{g,d}\right)_{\partial\mathcal{D}},
    & \hat{\Omega}\cdot\hat{n}_b>0,\vec{r}\in\partial\mathcal{D} \\
    0,
    & \hat{\Omega}\cdot\hat{n}_b<0,\vec{r}\in\partial\mathcal{D}
  \end{cases},
\end{gather}
%
Boundary source term:
%
\begin{gather}
  \langle\bm{\Psi}^*,\bm{\Psi}\rangle^+ - \langle\bm{\Psi}^*,\bm{\Psi}^\text{inc}\rangle^- =
  \begin{cases}
    \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\Psi^*_{g,d},
    \hat{\Omega}_d\cdot\hat{n}_b\Psi_{g,d}\right)_{\partial\mathcal{D}},
    & \hat{\Omega}\cdot\hat{n}_b>0,\vec{r}\in\partial\mathcal{D} \\
    \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\Psi^*_{g,d},
    \hat{\Omega}_d\cdot\hat{n}_b\Psi^\text{inc}_{g,d}\right)_{\partial\mathcal{D}},
    & \hat{\Omega}\cdot\hat{n}_b<0,\vec{r}\in\partial\mathcal{D}
  \end{cases}, \label{eq:boundary-source}
\end{gather}
%
Reflecting boundary term:
%
\begin{gather}
  \langle\bm{\Psi}^*,\bm{\Psi}\rangle^+ - \langle\bm{\Psi}^*,\mathbb{B}\bm{\Psi}\rangle^- =
  \begin{cases}
    \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\Psi^*_{g,d},
    \hat{\Omega}_d\cdot\hat{n}_b\Psi_{g,d}\right),
    & \hat{\Omega}\cdot\hat{n}_b>0,\vec{r}\in\partial\mathcal{D}_s \\
    \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\Psi^*_{g,d},
    \hat{\Omega}_d\cdot\hat{n}_b\Psi_{g,d_r}\right),
    & \hat{\Omega}\cdot\hat{n}_b<0,\vec{r}\in\partial\mathcal{D}_s
  \end{cases},
  \shortintertext{where}
  \hat{\Omega}_{d_r} = \hat{\Omega}_d - 2(\hat{\Omega}_d\cdot\hat{n}_b)\hat{n}_b. \nonumber
\end{gather}

@@

Transport corrections to allow neutron diffusion methods to reproduce high-fidelity flux solutions
can be introduced by modifying the neutron diffusion equations.
In this work, we explored two options for applying
transport corrections to the neutron diffusion equations: applying
diffusion corrections or adding a drift correction term.

@@

>>>>

\noindent Time derivative term:
%
\begin{gather}
  \left(\left(\mathbb{I}+\bm{\tau}\mathbb{L}_1\right)\bm{\Psi}^*,
  \frac{\partial}{\partial t}\left(\frac{\bm{\Psi}}{\bm{v}}\right)\right) =
  \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\Psi^*_{g,d}+\tau_g\hat{\Omega}_d\cdot\Psi^*_{g,d},
  \frac{\Psi_{g,d}}{v_g}\right)_\mathcal{D} \label{eq:time-derivative}
\end{gather}
%
Streaming term:
%
\begin{gather}
  \left(\mathbb{L}_1\bm{\Psi}^*,
  \left(\bm{\tau}\mathbb{L}_1-\mathbb{I}+\bm{\tau}\mathbb{L}_2\right)\bm{\Psi}\right) =
  \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\hat{\Omega}_d\cdot\nabla\Psi^*_{g,d},\tau_g\hat{\Omega}
  \cdot\nabla\Psi_{g,d}-(1-\tau_g\Sigma_{t,g})\Psi_{g,d}\right)_\mathcal{D}
\end{gather}
%
Collision term:
%
\begin{gather}
  \left(\mathbb{L}_2\bm{\Psi}^*,\bm{\Psi}\right) =
  \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\Psi^*_{g,d},\Sigma_{t,g}\Psi_{g,d}\right)_\mathcal{D}
\end{gather}
%
Scattering term:
%
\begin{gather}
  \left(\left(\mathbb{I}+\bm{\tau}\mathbb{L}_1\right)\bm{\Psi}^*,\mathbb{S}\bm{\Psi}\right) =
  \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\Psi^*_{g,d}+\tau_g\hat{\Omega}_d\cdot\nabla\Psi^*_{g,d},
  \sum^G_{g'=1}\sum^L_{l=0}\Sigma^{g'\rightarrow g}_{s,l}\sum^l_{m=-l}
  \frac{2l+1}{w}Y_{l,m}(\hat{\Omega}_d)\phi_{g',l,m}\right)_\mathcal{D}
\end{gather}
%
Prompt fission source term:
%
\begin{gather}
  \left(\left(\mathbb{I}+\bm{\tau}\mathbb{L}_1\right)\bm{\Psi}^*,\mathbb{F}\bm{\Psi}\right) =
  \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\Psi^*_{g,d}+\tau_g\hat{\Omega}_d\cdot\nabla\Psi^*_{g,d},
  \frac{1}{w}\bar{\chi}_g\sum^G_{g'=1}\nu\Sigma_{f,g'}\phi_{g'}\right)_\mathcal{D}
\end{gather}
%
where $\bar{\chi}_g=\chi_{p,g}\left(1-\beta\right)$ for time-dependent problems with \glspl{DNP}
and $\bar{\chi}_g=\chi_{g}$ for steady-state problems without \glspl{DNP}.

@@

\noindent Vacuum boundary term:
%
\begin{gather}
  \langle\bm{\Psi}^*,\bm{\Psi}\rangle^+ - \langle\bm{\Psi}^*,\bm{\Psi}^\text{inc}\rangle^- =
  \begin{cases}
    \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\Psi^*_{g,d},
    \hat{\Omega}_d\cdot\hat{n}_b\Psi_{g,d}\right)_{\partial\mathcal{D}},
    & \hat{\Omega}\cdot\hat{n}_b>0,\vec{r}\in\partial\mathcal{D} \\
    0,
    & \hat{\Omega}\cdot\hat{n}_b<0,\vec{r}\in\partial\mathcal{D}
  \end{cases},
\end{gather}
%
Boundary source term:
%
\begin{gather}
  \langle\bm{\Psi}^*,\bm{\Psi}\rangle^+ - \langle\bm{\Psi}^*,\bm{\Psi}^\text{inc}\rangle^- =
  \begin{cases}
    \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\Psi^*_{g,d},
    \hat{\Omega}_d\cdot\hat{n}_b\Psi_{g,d}\right)_{\partial\mathcal{D}},
    & \hat{\Omega}\cdot\hat{n}_b>0,\vec{r}\in\partial\mathcal{D} \\
    \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\Psi^*_{g,d},
    \hat{\Omega}_d\cdot\hat{n}_b\Psi^\text{inc}_{g,d}\right)_{\partial\mathcal{D}},
    & \hat{\Omega}\cdot\hat{n}_b<0,\vec{r}\in\partial\mathcal{D}
  \end{cases}, \label{eq:boundary-source}
\end{gather}
%
Reflecting boundary term:
%
\begin{gather}
  \langle\bm{\Psi}^*,\bm{\Psi}\rangle^+ - \langle\bm{\Psi}^*,\mathbb{B}\bm{\Psi}\rangle^- =
  \begin{cases}
    \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\Psi^*_{g,d},
    \hat{\Omega}_d\cdot\hat{n}_b\Psi_{g,d}\right),
    & \hat{\Omega}\cdot\hat{n}_b>0,\vec{r}\in\partial\mathcal{D}_s \\
    \sum^G_{g=1}\sum^{N_d}_{d=1}w_d\left(\Psi^*_{g,d},
    \hat{\Omega}_d\cdot\hat{n}_b\Psi_{g,d_r}\right),
    & \hat{\Omega}\cdot\hat{n}_b<0,\vec{r}\in\partial\mathcal{D}_s
  \end{cases}, \label{eq:reflecting-bc}
  \shortintertext{where}
  \hat{\Omega}_{d_r} = \hat{\Omega}_d - 2(\hat{\Omega}_d\cdot\hat{n}_b)\hat{n}_b. \nonumber
\end{gather}

@@

Transport corrections to allow neutron diffusion methods to reproduce high-fidelity flux solutions
can be introduced by modifying the neutron diffusion equations.
In this work, I explored two options for applying
transport corrections to the neutron diffusion equations: applying
diffusion corrections or adding a drift correction term.
I performed preliminary investigations on 1-D test cases with both types of transport correction. I
eventually elected to use the drift correction term for the remaining test cases and reactor model
demonstrations due to superior numerical properties. I will make clear the reasons for this
selection through 1-D test case results in Chapter 5.

@@

In this section, I detail the numerical implementation of the hybrid $S_N$-diffusion method with
drift correction terms. As mentioned in Section \ref{sec:transport-correction}, I opted for the
drift correction terms over diffusion correction for investigations beyond 1-D test cases.
Therefore, for brevity, I moved numerical implementation details for the hybrid method with
diffusion correction to Appendix A.

In Section \ref{sec:moltres-description}, I detailed the code structure of Moltres
\cite{lindsay_moltres_2017} in relation to the underlying \gls{MOOSE} finite-element framework
\cite{giudicelli_30_2024} and the pre-existing multigroup neutron diffusion and thermal-hydraulics
models. I implemented the hybrid $S_N$-diffusion model in Moltres to
leverage existing capabilities and functions that are also relevant to the new $S_N$ neutron
transport model and the $S_N$-to-diffusion coupling features. I also leveraged several basic
functions from \gls{MOOSE} that are useful for setting up physics models.

All source code for the hybrid $S_N$-diffusion model can be found in my Moltres GitHub fork
repository\footnote{\url{https://github.com/smpark7/moltres/tree/sn-method}} as of the time of
writing. This branch may be merged into the original upstream Moltres GitHub repository in future.

Moltres presently comes with a Python script for parsing and extracting neutron group constant data
from OpenMC \cite{boyd_multigroup_2019} or Serpent 2 \cite{leppanen_serpent_2014} simulation
output files. The script reorganizes the group constant data into a
JSON format file. I expanded the Python script to extract
the macroscopic total cross sections $\Sigma_{t,g}$ and the higher-order macroscopic Legendre
scattering moments $\Sigma^{g'\rightarrow g}_{s,l}$ for the $S_N$ neutron transport model. A new
\texttt{Material} class called \texttt{MoltresSNMaterial} creates material
property variables for each group constant for the $S_N$ model to read during a neutronics
simulation. If the user provides group constant data at multiple reactor temperature states,
\texttt{MoltresSNMaterial} can interpolate the data to simulate temperature-dependent reactivity
changes.

The new \texttt{MoltresUtils} class contains ``utility'' functions required by the $S_N$ model.
These functions include: a function to retrieve directions and weights defined by a
level-symmetric quadrature set of order $N$, a function to retrieve reflecting directions at
reflecting boundaries, and a function to compute spherical harmonic flux moments for anisotropic
scattering. I pre-computed the direction and weight values for the level-symmetric quadrature sets
using a Python script and hard-coded them in Moltres to reduce computational burden during
simulations.

The \gls{SAAF} $S_N$ method defines $G$ energy groups and $N_d$ discrete directions for a total
of $G\times N_d$ angular flux variables $\Psi_{g,d}$. The Moltres $S_N$ model groups the
$\Psi_{g,d}$ variables by energy group into $G$ \textit{array variables}. An array variable is a
set of standard field variables to help with dealing with setting up simulations with high
dimensionality. Each standard variable of an array variable is referred to as a component in the
array variable. In this work, I opted for
2nd-order Lagrange shape functions to approximate the $\Psi_{g,d}$ variables in the finite-element
analysis. The 2nd-order approximation showed better convergence rates in mesh refinement studies.

The terms in the \gls{SAAF} $S_N$ equations (Eqs.\ \ref{eq:time-derivative}-\ref{eq:reflecting-bc})
are represented by kernel and BC classes inheriting from \texttt{ArrayKernel} and
\texttt{ArrayIntegratedBC} template classes. Table \ref{tab:saaf-sn} lists the class names
corresponding to each term in Eq.\ \ref{eq:saaf-vt}.
%
\begin{table}[htb]
  \centering
  \caption{Names of the Kernels and BCs representing the \gls{SAAF} $S_N$ equations.}
  \begin{tabular}{l l l}
    \toprule
    Term name & Class name \\
    \midrule
    Time derivative & \texttt{SNTimeDerivative} \\
    Streaming & \texttt{SNStreaming} \\
    Collision & \texttt{SNCollision} \\
    Scattering & \texttt{SNScattering} \\
    Prompt fission source & \texttt{SNFission} \\
    Delayed neutron source & \texttt{SNDelayed} \\
    Vacuum boundary & \texttt{SNVacuumBC} \\
    Reflecting boundary & \texttt{SNReflectingBC} \\
    Hybrid method boundary source & \texttt{SNDiffusionBC} \\
    \bottomrule
  \end{tabular}
  \label{tab:saaf-sn}
\end{table}

The \gls{MOOSE} framework leverages the Eigen \cite{guennebaud_eigen_2010} C++ template library for
linear algebra operations defined in ArrayKernels and ArrayBCs for array variables. The \gls{SAAF}
$S_N$ kernels and BCs contain functions for computing the residual and Jacobian contributions of
each term. The \gls{FEM} numerical solver deems to have reached a converged solution if the sum of
residual contributions falls below a defined tolerance value. All $S_N$ simulations in this work
employ the \gls{PJFNK} method with the HYPRE-BoomerAMG method for preconditioning. BoomerAMG is an
algebraic multigrid method from the HYPRE \cite{hypre_hypre_2022} linear solver library.

The drift correction terms $\vec{D}_g$ are initialized as auxiliary array variables
with three components corresponding to their $x$, $y$, and $z$ components. Auxiliary variables
encompass all field variables which are not directly determined during the \gls{PJFNK}
calculation stage. The drift and boundary correction variables are computed during the
post-calculation stage from $\Psi_{g,d}$.

I employed the \texttt{MultiApp} system \cite{gaston_physics-based_2015} to implement the fixed point
iterative coupling between the $S_N$ and neutron diffusion solvers for the hybrid $S_N$-diffusion method.
The \texttt{MultiApp} and \texttt{Transfers} systems from \gls{MOOSE} provide flexible interfaces
for setting up iterative solvers and transferring data between the solvers. A typical hybrid
method simulation on Moltres starts with the neutron diffusion solver for the first estimate of the
neutron flux distribution. Moltres transfers the neutron flux distribution to the $S_N$ solver to
compute the boundary source distribution. The $S_N$ solver then generates its own flux estimate and
computes drift and boundary correction variables for the neutron diffusion solver. Moltres
transfers the correction variables to the neutron diffusion solver to compute its next flux
estimate. This process continues until the neutron flux distribution converges to within tolerance
values provided in the input file.

### 2024-06-20 lit.tex
add verification chapter for referencing, hybrid chapter edits
Fix typos and add numerical implementation section

Others adopted extensible software frameworks for developing numerical solvers
to develop multiphysics reactor analysis software. Examples of these software
frameworks include the commercial COMSOL
Multiphysics\textsuperscript{\textregistered} software
\cite{comsol_ab_comsol_nodate}, the aforementioned open-source CFD toolbox
OpenFOAM, and the open-source finite-element
framework \gls{MOOSE} \cite{gaston_physics-based_2015}. Researchers at
\gls{PoliMi} developed an \gls{MSR} simulation tool in COMSOL and
modeled the \gls{MSBR} as a single axisymmetric fuel channel with a uniform
flow profile \cite{cammi_multi-physics_2011}, followed by the \gls{MSRE} core
also as a single axisymmetric fuel channel with parabola-shaped laminar flow
\cite{cammi_dimensional_2012}. They later expanded on their approach by
modeling the \gls{MSRE} upper plenum, downcomer and lower plenum, primary heat
exchanger, and secondary heat exchanger as 0D systems (lumped-parameter model)
and substituting the 2-D fuel channel with a 3-D fuel channel which more closely
resembled the actual fuel channels in the \gls{MSRE}
\cite{zanetti_geometric_2015}. Other than the \gls{MSRE}, they also modeled the
\gls{MSFR} in a later publication \cite{fiorina_modelling_2014}, which also featured \gls{TUD}'s
DALTON-HEAT coupled multiphysics tool.

@@

Two recent works by Anistratov \& Stehle \cite{anistratov_computational_2012} and Stehle et al.\
\cite{stehle_hybrid_2014} describe another approach that is distinct from the prior approach in
two ways. Firstly, they developed an on-the-fly scheme for estimating a transport metric which can
indicate whether a subregion is diffusive. The solver uses this information to apply adaptive
domain decomposition and decide which subregions require transport calculations for solution
accuracy. Secondly, they employ a two-level neutronics method similar to the multilevel \gls{QD}
method to obtain the neutron flux solution. The hybrid method evaluates the low-order neutron
diffusion problem on the entire problem domain while limiting high-order transport calculations to
\textit{transport} subregions. The low-order formulation also serves as an acceleration scheme to
the high-order formulation to provide greater computational cost savings. The authors showed the
viability of using Eddington tensor estimates as the metric for quantifying transport effects in
a subregion. The Eddington tensor is identical to one defined for the \gls{QD} scheme. The
two-level neutronics method is based on the \textit{Second-Moment} method developed by Lewis \&
Miller \cite{lewis_comparison_1976}. The low-order second-moment equations are:
%
\begin{gather}
  \nabla\cdot J^{(s+1)}+\Sigma_a\phi^{(s+1)} = q, \\
  \frac{1}{3}\nabla\cdot\phi^{(s+1)}+\Sigma_t J^{(s+1)} = \nabla\cdot F^{(s+1/2)}
  \shortintertext{where}
  F^{(s+1/2)}_{\alpha\beta} = \int_{4\pi}
  \left(\frac{1}{3}\delta_{\alpha\beta}-\Omega_\alpha\Omega_\beta\right)
  \Psi^{(s+1/2)} d\Omega
\end{gather}
%
$(s)$ denotes the iteration index. $F$ is a transport correction tensor calculated from the
high-order neutron transport equations in \textit{transport} subregions. $F$ is simply set to zero
in \textit{diffusive} subregions. The scalar flux from the low-order equations is also used to
evaluate the 0th-order scattering source term and accelerate the high-order calculations for
$\Psi^{(s+1/2)}$. Stehle et al.\ \cite{stehle_hybrid_2014} demonstrated their hybrid method on two
2-D, single-group test problems. Both problems consisted of two regions with idealized macroscopic
cross sections representing \textit{transport} and \textit{diffusive} regions with high absorption
and scattering ratios, respectively.

>>>>

Others adopted extensible software frameworks for developing numerical solvers
to develop multiphysics reactor analysis software. Examples of these software
frameworks include the commercial COMSOL
Multiphysics\textsuperscript{\textregistered} software
\cite{comsol_ab_comsol_nodate}, the aforementioned open-source CFD toolbox
OpenFOAM, and the open-source finite-element
framework \gls{MOOSE} \cite{giudicelli_30_2024}. Researchers at
\gls{PoliMi} developed an \gls{MSR} simulation tool in COMSOL and
modeled the \gls{MSBR} as a single axisymmetric fuel channel with a uniform
flow profile \cite{cammi_multi-physics_2011}, followed by the \gls{MSRE} core
also as a single axisymmetric fuel channel with parabola-shaped laminar flow
\cite{cammi_dimensional_2012}. They later expanded on their approach by
modeling the \gls{MSRE} upper plenum, downcomer and lower plenum, primary heat
exchanger, and secondary heat exchanger as 0D systems (lumped-parameter model)
and substituting the 2-D fuel channel with a 3-D fuel channel which more closely
resembled the actual fuel channels in the \gls{MSRE}
\cite{zanetti_geometric_2015}. Other than the \gls{MSRE}, they also modeled the
\gls{MSFR} in a later publication \cite{fiorina_modelling_2014}, which also featured \gls{TUD}'s
DALTON-HEAT coupled multiphysics tool.

@@

Two recent works by Anistratov \& Stehle \cite{anistratov_computational_2012} and Stehle et al.\
\cite{stehle_hybrid_2014} describe another approach that is distinct from the prior approach in
two ways. Firstly, they developed an on-the-fly scheme for estimating a transport metric which can
indicate whether a subregion is diffusive. The solver uses this information to apply adaptive
domain decomposition and decide which subregions require transport calculations for solution
accuracy. Secondly, they employ a two-level neutronics method similar to the multilevel \gls{QD}
method to obtain the neutron flux solution. The hybrid method evaluates the low-order neutron
diffusion problem on the entire problem domain while limiting high-order transport calculations to
\textit{transport} subregions. The low-order formulation also serves as an acceleration scheme to
the high-order formulation to provide greater computational cost savings. The authors showed the
viability of using Eddington tensor estimates as the metric for quantifying transport effects in
a subregion. The Eddington tensor is identical to one defined for the \gls{QD} scheme. The
two-level neutronics method is based on the \textit{Second-Moment} method developed by Lewis \&
Miller \cite{lewis_comparison_1976}. The low-order second-moment equations are:
%
\begin{gather}
  \nabla\cdot J^{(s+1)}+\Sigma_a\phi^{(s+1)} = q, \label{eq:2nd-moment-1} \\
  \frac{1}{3}\nabla\cdot\phi^{(s+1)}+\Sigma_t J^{(s+1)} = \nabla\cdot F^{(s+1/2)}
  \label{eq:2nd-moment-2}
  \shortintertext{where}
  F^{(s+1/2)}_{\alpha\beta} = \int_{4\pi}
  \left(\frac{1}{3}\delta_{\alpha\beta}-\Omega_\alpha\Omega_\beta\right)
  \Psi^{(s+1/2)} d\Omega \label{eq:2nd-moment-3}
\end{gather}
%
$(s)$ denotes the iteration index. $F$ is a transport correction tensor calculated from the
high-order neutron transport equations in \textit{transport} subregions. $F$ is simply set to zero
in \textit{diffusive} subregions. The scalar flux from the low-order equations is also used to
evaluate the 0th-order scattering source term and accelerate the high-order calculations for
$\Psi^{(s+1/2)}$. Stehle et al.\ \cite{stehle_hybrid_2014} demonstrated their hybrid method on two
2-D, single-group test problems. Both problems consisted of two regions with idealized macroscopic
cross sections representing \textit{transport} and \textit{diffusive} regions with high absorption
and scattering ratios, respectively.
